### 2015-11-07 Assignment IV/Assignment4-Ditz_Schroeder-WS15-16.tex
update of .tex file

\begin{figure}[ht]
 \centering
 \subfigure{
 \begin{tabular}{c|ccc}
  \textit{total column score} & \textbf{Clustal$\Omega$} & \textbf{MUSCLE} & \textbf{MAFFT} \\
  \hline
  \textbf{BB11007} & 0.33 & 0.39 & 0.24 \\
  \textbf{BB20002} & 0.00 & 0.00 & 0.00 \\
  \textbf{Prolyl-tRNA} & $c_{1,3}$ & $c_{2,3}$ & $c_{3,3}$ \\
 \end{tabular}}
 \caption{total column score of all used programs for example files}
 \label{totCol}
\end{figure}

\begin{figure}[ht]
 \centering
 \subfigure{
 \begin{tabular}{c|ccc}
   \textit{SP-score}& \textbf{Clustal$\Omega$} & \textbf{MUSCLE} & \textbf{MAFFT} \\
  \hline
  \textbf{BB11007} & 0.597 & 0.582 & 0.524 \\
  \textbf{BB20002} & 0.314 & 0.197 & 0.246 \\
  \textbf{Prolyl-tRNA} & $s_{1,3}$ & $s_{2,3}$ & $s_{3,3}$ \\
 \end{tabular}}
 \caption{sum-of-pairs score of all used programs for example files}
 \label{SPscore}
\end{figure}

\begin{figure}[ht]
 \centering
 \subfigure{
 \begin{tabular}{c|ccc}
  \textit{runtime} & \textbf{Clustal$\Omega$} & \textbf{MUSCLE} & \textbf{MAFFT} \\
  \hline
  \textbf{BB11007} & $t_{1,1}$ & $t_{2,1}$ & $t_{3,1}$ \\
  \textbf{BB20002} & $t_{1,2}$ & $t_{2,2}$ & $t_{3,2}$ \\
  \textbf{Prolyl-tRNA} & $t_{1,3}$ & $t_{2,3}$ & $t_{3,3}$ \\
 \end{tabular}}
 \caption{runtime of all used programs for example files}
 \label{runtime}
\end{figure}

>>>>

\begin{figure}[ht]
 \centering
 \subfigure{
 \begin{tabular}{c|ccc}
  \textit{total column score} & \textbf{Clustal$\Omega$} & \textbf{MUSCLE} & \textbf{MAFFT} \\
  \hline
  \textbf{BB11007} & 0.33 & 0.39 & 0.24 \\
  \textbf{BB20002} & 0.00 & 0.00 & 0.00 \\
  \textbf{Prolyl-tRNA} & $c_{1,3}$ & $c_{2,3}$ & $c_{3,3}$ \\
 \end{tabular}}
 \caption{total column score of all alignments}
 \label{totCol}
\end{figure}

\begin{figure}[ht]
 \centering
 \subfigure{
 \begin{tabular}{c|ccc}
   \textit{SP-score}& \textbf{Clustal$\Omega$} & \textbf{MUSCLE} & \textbf{MAFFT} \\
  \hline
  \textbf{BB11007} & 0.597 & 0.582 & 0.524 \\
  \textbf{BB20002} & 0.314 & 0.197 & 0.246 \\
  \textbf{Prolyl-tRNA} & $s_{1,3}$ & $s_{2,3}$ & $s_{3,3}$ \\
 \end{tabular}}
 \caption{sum-of-pairs score of all alignments}
 \label{SPscore}
\end{figure}

\begin{figure}[ht]
 \centering
 \subfigure{
 \begin{tabular}{c|ccc}
  \textit{runtime} & \textbf{Clustal$\Omega$} & \textbf{MUSCLE} & \textbf{MAFFT} \\
  \hline
  \textbf{BB11007} & 0.389 & 0.488 & 0.13 \\
  \textbf{BB20002} & 6.62 & 19.928 & 0.38 \\
  \textbf{Prolyl-tRNA} & $t_{1,3}$ & $t_{2,3}$ & $t_{3,3}$ \\
 \end{tabular}}
 \caption{runtime of all used programs for example files (in sec)}
 \label{runtime}
\end{figure}
